quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-09-18 paper-quollr.tex
Updated function outputs

The result is a data frame of the scaled $2\text{-}D$ embedding with an additional \texttt{h} column, indicating the hexagonal bin to which each point belongs.

>>>>

The result is a \texttt{tibble} of the scaled $2\text{-}D$ embedding with an additional \texttt{h} column, indicating the hexagonal bin to which each point belongs.
